CS6213 Project Report

### 2021-05-07 report/paper.tex
Add more findings

    \item We started developing a prototype testing framework on top of \etcd to simulate execution traces generated by TLC.

@@

@@

We did not find any bugs in the implementation, only specification omissions.

>>>>

@@

    \item We developed a prototype testing framework on top of \etcd to simulate execution traces generated by TLC against their actual Raft implementation, covering a representative subset of Raft's functionality.
    %
    This led to us discovering more specification omissions.

    \item We outlined a number of guidelines which we believe are applicable to any implementation of the same approach.

    \item We believe model-based test case generation is a promising approach, with its main deterrent being the amount of effort required to carefully model every detail of a mature implementation. Still, it does not require specialised knowledge and does provide the link between model and implementation we hoped for.

@@

We did not find any bugs in the implementation, only specification omissions, and arguably rather specific to \etcd's behaviour.
